equations

### 2023-05-22 equations.Rmd
updates

---
title: "equations"
author: "Jesper Fischer Ehmsen"
date: "`r Sys.Date()`"
output: html_document
---

@@

$$
\begin{equation}
\tag{5}
S_t \sim \mathcal{N}{(\mu_{p_t}, \sigma_s^2)}
\end{equation}
$$

@@

$$
\begin{equation}
\tag{8}
E_t | S_{{t-1}} \sim \mathcal{N}{(E_{t-1}, \sigma_E^2)}
\end{equation}
$$
Now combining (8) and (6) we get a prior for the precept at a given trial, which is before getting the stimulus but after getting the cue

$$
\begin{equation}
\tag{9}
\psi_t | S_{{t-1}} \sim \mathcal{N}{(E_{t-1}, \sigma_E^2+ \sigma_{\psi}^2))}
\end{equation}
$$

@@

$$
\begin{equation}
\tag{9}
\psi_t | S_{{t-1}} \sim \mathcal{N}{(\frac{\sigma_{s}^2*E_t+(\sigma_{\psi}^2+\sigma_E^2)*S_t}{\sigma_{s}^2+\sigma_{\psi}^2+\sigma_E^2}, \frac{\sigma_{s}^2+\sigma_{\psi}^2+\sigma_E^2}{\sigma_{s}^2*(\sigma_{\psi}^2+\sigma_E^2)}})
\end{equation}
$$
The mean rating of the agent on trial t is therefore given by the mean, which can also be writting as:

$$
\begin{equation}
\tag{9}
\mu_{\psi_t} = \frac{\sigma_{s}^2}{\sigma_{s}^2+\sigma_{\psi}^2+\sigma_E^2}*E_t+\frac{(\sigma_{\psi}^2+\sigma_E^2)}{\sigma_{s}^2+\sigma_{\psi}^2+\sigma_E^2}*S_t
\end{equation}
$$

@@

$$
\begin{equation}
\tag{7}
E_{t+1}|S_t \sim \mathcal{N}{(\frac{(\sigma_{s}^2+\sigma_{\psi}^2)*E_{t-1}+\sigma_E^2*S_t}{\sigma_{s}^2+\sigma_{\psi}^2+\sigma_E^2}, \frac{(\sigma_{s}^2+\sigma_{\psi}^2)*\sigma_E^2}{\sigma_{s}^2+\sigma_{\psi}^2+\sigma_E^2}+\sigma_\eta^2})
\end{equation}
$$

see equation (1)

$$
\begin{equation}
\tag{*}
beinf(y;p_0,p_1,\mu,\phi) = \begin{cases}
      p_0 & x = 0 \\
      f(y;\mu,\phi) & x \in (0,1) \\
      p_1 & x = 1 
   \end{cases}
\end{equation}
$$

where the probability density function of the beta distribution $f(y;\mu,\phi)$ is given by

$$
f(y;\mu,\phi) = \frac{\Gamma(\alpha+\beta)}{\Gamma(\alpha)\Gamma(\beta)}y^{\alpha-1}(1-y)^{\beta-1},y\in (0,1)
$$

In the current study using the GAMLSS packages the parameters are reparameterized as follows:

$$ 
\mu = \frac{\alpha}{\alpha+\beta}
$$

$$
\sigma = \frac{1}{\alpha+\beta+1}
$$

$$
\tau = \frac{p_0}{p_2}
$$

$$
\nu = \frac{p_1}{p_2}
$$
where $p_2 = 1-p_0-p_1$

>>>>

---
title: "equations"
author: "Jesper Fischer Ehmsen"
date: "`r Sys.Date()`"
output:
  word_document: default
  html_document: default
---

@@

$$
\begin{equation}
\tag{5}
S_t \sim \mathcal{N}{(\psi{_t}, \sigma_s^2)}
\end{equation}
$$

@@

$$
\begin{equation}
\tag{8}
E_t | S_{{t-1}} \sim \mathcal{N}{(\mu_{E_{t-1}}, \sigma_{E_t}^2)}
\end{equation}
$$
Now combining (8) and (6) we get a prior for the precept at a given trial, which is before getting the stimulus but after getting the cue

$$
\begin{equation}
\tag{9}
\psi_t | S_{{t-1}} \sim \mathcal{N}{(\mu_{E_{t-1}}, \sigma_{E_t}^2+ \sigma_{\psi}^2))}
\end{equation}
$$

@@

$$
\begin{equation}
\tag{10}
\psi_t | S_{{t}} \sim \mathcal{N}{(\frac{\sigma_{s}^2*\mu_{E_{t-1}}+(\sigma_{\psi}^2+\sigma_{E_t}^2)*S_t}{\sigma_{s}^2+\sigma_{\psi}^2+\sigma_{E_t}^2}, \frac{\sigma_{s}^2+\sigma_{\psi}^2+\sigma_{E_t}^2}{\sigma_{s}^2*(\sigma_{\psi}^2+\sigma_{E_t}^2)}})
\end{equation}
$$
The mean rating of the agent on trial t is therefore given by the mean, which can also be writting as:

$$
\begin{equation}
\tag{11}
\mu_{\psi_t} = \frac{\sigma_{s}^2}{\sigma_{s}^2+\sigma_{\psi}^2+\sigma_{E_t}^2}*\mu_{E_{t-1}}+\frac{\sigma_{\psi}^2+\sigma_{E_t}^2}{\sigma_{s}^2+\sigma_{\psi}^2+\sigma_{E_t}^2}*S_t
\end{equation}
$$

@@

$$
\begin{equation}
\tag{12}
E_{t}|S_t \sim \mathcal{N}{(\frac{(\sigma_{s}^2+\sigma_{\psi}^2)*\mu_{E_{t-1}}+\sigma_{E_t}^2*S_t}{\sigma_{s}^2+\sigma_{\psi}^2+\sigma_{E_t}^2}, \frac{(\sigma_{s}^2+\sigma_{\psi}^2)*\sigma_{E_t}^2}{\sigma_{s}^2+\sigma_{\psi}^2+\sigma_{E_t}^2}+\sigma_\eta^2})
\end{equation}
$$

It can be shown that these update equations for the expectation and the mean percept are a generalization of the above mentioned RW model if we define two trial by trial parameters $\gamma_{t}$ and $\alpha_{t}$

$$
\begin{equation}
\tag{13}
\gamma_{t} = \frac{\sigma_{s}^2}{\sigma_{s}^2+\sigma_{\psi}^2+\sigma_{E_t}^2}
\end{equation}
$$
$$
\begin{equation}
\tag{14}
\alpha_{t} = \frac{\sigma_{E_t}^2}{\sigma_{\psi}^2+\sigma_{E_t}^2}
\end{equation}
$$

one can arrive at the following update equations for the percept and the expectation

$$
\begin{equation}
\tag{15}
\psi_{t} = (1-\gamma_{t})*S_{t}+\gamma_{t}*E_{t}
\end{equation}
$$

$$
\begin{equation}
\tag{16}
E_{t} = \alpha_{t}*\psi_{t}+(1-\alpha_{t})*E_{t}
\end{equation}
$$
For the derivation of equation 15 and 16 readers are refereed to the supplementary material.
